Nathan Greenslit Data Analysis Project

### 2023-04-07 code/analysis_code/stats/4_uni_variate.qmd
edited questions

fig3<- rd2 %>% ggplot(aes(lag, copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "pearson")+
  labs(title = "LM DustxCopies (RD+2)",
       x = "log(dust)")
```

@@

aug_test_rd <- augment(growth_fit_rd, rd2)
rmse <- aug_test_rd %>% rmse(truth = copies_mL, .pred)
rsq <- aug_test_rd %>% rsq(truth = copies_mL, .pred)
rd_metrics<- full_join(rmse, rsq)
rd_metrics
```

>>>>

fig3<- rd2 %>% ggplot(aes(lag, copies_mL)) +
  geom_point() +
  stat_smooth(method = "lm")+
  stat_correlation(method = "pearson")+
  labs(title = "LM DustxCopies (RD+1)",
       x = "log(dust)")
```

@@

aug_test_rd <- augment(growth_fit_rd, rd2)
rmse <- aug_test_rd %>% rmse(truth = copies_mL, .pred)
rsq <- aug_test_rd %>% rsq(truth = copies_mL, .pred)
rd_metrics<- full_join(rmse, rsq)
rd_metrics

### 2023-04-07 products/manuscript/Manuscript.qmd
edited questions

1.  Does my overall workflow in `code/analysis_code/stats/3_uni_variate.qmd` make sense? Is there anything that I am missing, or be a better option for analysis?

@@

    -   If this looks good, I plan to do the same workflow for all of the environmental parameters as well. For now, I just have plots to see what may be worth diving into.

2.  Looking at `code/analysis_code/stats/4_multi_variate.qmd` , I am a little stuck on how to best create a multivariate model.

@@

3.  Ultimately, I feel as though I am missing some "oomph"when it comes to my statistical analysis. The linear models seem adequate, but I know that there are multiple variables at play at these sites (and we have data to explore some of this). I am open to any suggestions that may diversify and expand my analyses!

4.  In my `code/analysis_code/stats/3_uni_variate.qmd` code I was playing around with R2 for my linear models. Previously I have been plotting R2 onto the graphs using `stat_poly_equation()` but then I came across the `stat_correlation()` command. When specifying "pearson" as the method, I get a MUCH higher R2 value for the models (\~0.48 to \~0.70). I have been trying to figure out what `stat_poly_equation` uses as its method and why there is such a difference. At least with dust and copies_mL, I expect Pearson's to be a good method. But is there some serious error that I am making here?

>>>>

1.  In my `code/analysis_code/stats/3_uni_variate.qmd` code I was playing around with R2 for my linear models. Previously I have been plotting R2 onto the graphs using `stat_poly_equation()` and have also checked through `tidymodeling`. But then I came across the `stat_correlation()` command. When specifying "pearson" as the method, I get a **MUCH** higher R2 value for the models (\~0.48 to \~0.70). I have been trying to figure out what `stat_poly_equation` uses as its method and why there is such a difference. Additionally, my actual model produces the same lower R2 values (using `rsq()`) as the `stat_poly_equation()`. Is there some serious error that I am making here?

2.  Does my overall workflow in `code/analysis_code/stats/3_uni_variate.qmd` make sense? Is there anything that I am missing, or be a better option for analysis?

@@

    -   If this looks good, I plan to do the same workflow for all of the environmental parameters (that seem to have a relationship) as well. For now, I just have plots to see what may be worth diving into.

3.  Looking at `code/analysis_code/stats/4_multi_variate.qmd` , I am a little stuck on how to best create a multivariate model.

@@

4.  Ultimately, I feel as though I am missing some "oomph" when it comes to my statistical analysis. The linear models seem adequate, but I know that there are multiple variables at play at these sites (and we have data to explore some of this). I am open to any suggestions that may diversify and expand my analyses! I am thinking some sort of PCA that depicts which predictor variables have the greatest influence on the outcome.
